\chapter*{Acknowledgements}
\thispagestyle{empty}
First and foremost thanks must be given to my academic supervisor Professor Neil McCauley, someone whose intelligence, work ethic and kindness have continously been a source of inspiration to me. 

I am also forever indebted to a number of postdoctoral researchers who I was fortunate enough to have aid me with my research; namely Dr Ka Ming Tsui, Dr Pablo Fernandez Menendez, Dr Lauren Anthony, Dr Adrian Pritchard and Dr Samuel Jamuel Jenkins. Thank you all for your continued encouragement and support, and apologies for emailing all of you for help so much (but in my defence ROOT is the worst).

I am also incredibly grateful to members of the neutron tagging working group, in particular Dr Fabio Iacob whose weekly meetings about my analysis were crucial to my work and who is one of the most patient and kind individuals I have ever met (and I wouldn't have survived calculating the systematics without him). I am also indebted to Seungho Han for his help with the new neutron tagging software, and also Nakajima-sensei, Koshio-sensei, Akutsu-sensei and Tairafune-san for their input in the neutron tagging meetings. 

I'd also like to thank current and former members of the Super-Kamiokande and Hyper-Kamiokande calibration groups, Dr Jordan McElwee, Dr Matthew Thiesse, Dr Billy Vinning and Yang-san for UKLI MC implementation help. 
 
A huge thank you to Dr Gedminas Elertas, who has been a source of virtue and intellectual inspiration to me and has made me want to keep learning, not just with things relating to physics but outside of it too. The day-to-day of academic research sometimes ground me down a little internally, but you kept the spirit of scientific curiosity alive inside me, and I can't thank you enough for this. 

Many thanks to my wonderful besties from undergrad, Karel Green and Rachel Couchman, I've known both of you for nearly a decade and I treasure your friendship so so much, you've kept me sane and supported throughout this entire journey. Here's to you, babes!
Also to my schoolfriends Catherine Thomas, Amy Rose-Mansbridge and Catriona Bradley, I've known you for over 15 years and it has been incredible to see you all blossom into amazing, capable and talented young women who I'm blessed to know. Also thanks to Patrick Bates for the calmness and profound wisdom that you so often espouse, you wonderful lovely nerd! 

Thank you to Joseph (my \textit{imzadi}) for your gentle and kind heart, you've always been so incredibly supportive and I'm so happy to know you.  

To my parents, ``thank you'' isn't anywhere near a sufficient enough response to how much you've supported me. Mum - your strength and wisdom is unparalled, and dad, well, you're the best physicist I know. Finally to my sister Nidhi, who this thesis is dedicated to, I love you so much and your kindness and intelligence is something I aspire to everyday. You're amazing! 
